
---
title: "WVS: Hypothesis testing"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---

#Hypothesis 1: poor people more myopic
in comparison to high-income individuals

##Hypothesis 1a: poor people less general trust

##Hypothesis 1a: less general trust = more mypoia 

#Hypothesis 2: neighborhood trust not different 

```{r}

```


#Hypothesis 3: poor people with neighborhood trust less myopic 



```{r}
#neighborhood trust
fit1 <- lm(pc1 ~ nTrust, data = pca_val_data)
summary(fit1)

#neighborhood trust controlling for general trust (additave model... IVs very different)
fit2 <- lm(pc1 ~ nTrust + gTrust, data = pca_val_data)
summary(fit2)


#neighborhood trust controlling for general trust (interactions between IVs)
fit3 <- lm(pc1 ~ nTrust * gTrust, data = pca_val_data)
summary(fit3)

ntrust_subEffect <- effect("nTrust*gTrust", fit3)
summary(ntrust_subEffect)
plot(ntrust_subEffect, multiline=TRUE, rug=FALSE)

#boxplot(pc1~nTrust, data=pca_val_data)
```


##means of TD proxy
broken down by neighborhood trust and general trust
###including income 
```{r, echo=FALSE}
pca_NOincome %>% group_by(nTrust, gTrust) %>% 
  summarise(discounting_factor = mean(pc1, na.rm = T)) 
```

###NOT including income 
```{r, echo=FALSE}
pca_NOincome %>% group_by(nTrust, gTrust) %>% 
  summarise(discounting_factor = mean(pc1, na.rm = T)) 
```

