
---
title: "WVS: Hypothesis testing"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("/git_repositories/trust/WVS_data/scripts/load_libraries.R")
wvs_data <- readRDS("/git_repositories/trust/WVS_data/data/in_process_data/fulldata_cleaned.RDS")
pca_val_data <- read_csv("/git_repositories/trust/WVS_data/data/pca/pca_income.csv")
pca_val_dataNOINCOME <- read_csv("/git_repositories/trust/WVS_data/data/pca/pca_NOincome.csv")
```

#Hypothesis 1: poor people more myopic
...in comparison to high-income individuals. **indeed** found to be the case:

##poor = (≤ 4)
```{r, echo=FALSE}
hyp1 <- pca_val_dataNOINCOME %>% filter(!is.na(income)) %>%
          mutate(low_income = ifelse(income <=4, T, F)) %>%
          group_by(low_income) %>% 
          summarise(discounting_factor = mean(pc1, na.rm = T)) 
hyp1
```

##other definitions of poor
###poor = (≤ 3)
```{r, echo=FALSE}
hyp1 <- pca_val_dataNOINCOME %>% filter(!is.na(income)) %>%
          mutate(low_income = ifelse(income <=3, T, F)) %>%
          group_by(low_income) %>% 
          summarise(discounting_factor = mean(pc1, na.rm = T)) 
hyp1
```

###poor = (≤ 2)
```{r, echo=FALSE}
hyp1 <- pca_val_dataNOINCOME %>% filter(!is.na(income)) %>%
          mutate(low_income = ifelse(income <=2, T, F)) %>%
          group_by(low_income) %>% 
          summarise(discounting_factor = mean(pc1, na.rm = T)) 
hyp1
```

###poor = (≤ 1)
```{r, echo=FALSE}
hyp1 <- pca_val_dataNOINCOME %>% filter(!is.na(income)) %>%
          mutate(low_income = ifelse(income <=1, T, F)) %>%
          group_by(low_income) %>% 
          summarise(discounting_factor = mean(pc1, na.rm = T)) 
hyp1
```

\
[back to table of contents](#TOC)

#Hypothesis 1a: poor people less general trust

**indeed** in every definition of low income, there are as a percent within each group, less poor people that have general trust when compared to middle/high income individuals

##poor = (≤ 4)
```{r, echo=FALSE}
general <- wvs_data %>% filter(!is.na(gTrust), !is.na(income)) %>%
          select(gTrust, low_income = lowIncome_4) 
denoms <- general %>% group_by(low_income) %>% summarize(denoms = n()) 
general <- general %>% group_by(gTrust, low_income) %>% summarize(nums = n()) %>%
          mutate(total = ifelse(low_income, as.numeric(denoms[[2,2]]), as.numeric(denoms[[1,2]])),
                 percent = round(100*nums/total, digits = 2))
general %>% select(-c(nums:total)) %>% arrange(desc(low_income))

ggplot(data=general, aes(x=gTrust, y=percent , fill = low_income)) +
    geom_bar(stat="identity", position=position_dodge(), colour = "black") + 
  theme(legend.position="bottom", axis.text.x  = element_text(face="bold")) + 
  xlab("") + ggtitle("General Trust by Income")
```

##other definitions of poor
on the 1-10 income scale, we define poor as those that selected 3 or less etc...

###poor = (≤ 3)
```{r, echo=FALSE}
general <- wvs_data %>% filter(!is.na(gTrust), !is.na(income)) %>%
          select(gTrust, low_income = lowIncome_3) 
denoms <- general %>% group_by(low_income) %>% summarize(denoms = n()) 
general <- general %>% group_by(gTrust, low_income) %>% summarize(nums = n()) %>%
          mutate(total = ifelse(low_income, as.numeric(denoms[[2,2]]), as.numeric(denoms[[1,2]])),
                 percent = round(100*nums/total, digits = 2))
general %>% select(-c(nums:total)) %>% arrange(desc(low_income))

# ggplot(data=general, aes(x=gTrust, y=percent , fill = low_income)) +
#     geom_bar(stat="identity", position=position_dodge(), colour = "black") + 
#   theme(legend.position="bottom", axis.text.x  = element_text(face="bold")) + xlab("")
```

###poor = (≤ 2)
```{r, echo=FALSE}
general <- wvs_data %>% filter(!is.na(gTrust), !is.na(income)) %>%
          select(gTrust, low_income = lowIncome_2) 
denoms <- general %>% group_by(low_income) %>% summarize(denoms = n()) 
general <- general %>% group_by(gTrust, low_income) %>% summarize(nums = n()) %>%
          mutate(total = ifelse(low_income, as.numeric(denoms[[2,2]]), as.numeric(denoms[[1,2]])),
                 percent = round(100*nums/total, digits = 2))
general %>% select(-c(nums:total)) %>% arrange(desc(low_income))

# ggplot(data=general, aes(x=gTrust, y=percent , fill = low_income)) +
#     geom_bar(stat="identity", position=position_dodge(), colour = "black") + 
#   theme(legend.position="bottom", axis.text.x  = element_text(face="bold")) + xlab("")
```

###poor = (≤ 1)
```{r, echo=FALSE}
general <- wvs_data %>% filter(!is.na(gTrust), !is.na(income)) %>%
          select(gTrust, low_income = lowIncome_1) 
denoms <- general %>% group_by(low_income) %>% summarize(denoms = n()) 
general <- general %>% group_by(gTrust, low_income) %>% summarize(nums = n()) %>%
          mutate(total = ifelse(low_income, as.numeric(denoms[[2,2]]), as.numeric(denoms[[1,2]])),
                 percent = round(100*nums/total, digits = 2))
general %>% select(-c(nums:total)) %>% arrange(desc(low_income))

# ggplot(data=general, aes(x=gTrust, y=percent , fill = low_income)) +
#     geom_bar(stat="identity", position=position_dodge(), colour = "black") + 
#   theme(legend.position="bottom", axis.text.x  = element_text(face="bold")) + xlab("")
```

\
[back to table of contents](#TOC)

#Hypothesis 1b: less general trust = more mypoia 

**indeed** less general trust means more discounting

```{r, eval=FALSE}
# fit1 <- glm(as.factor(gTrust) ~ pc1, data = pca_val_dataNOINCOME, family = binomial())
# summary(fit1) 
pca_val_dataNOINCOME %>% group_by(gTrust) %>% 
  summarise(discounting_factor = mean(pc1, na.rm = T)) 
```

\
[back to table of contents](#TOC)

#Hypothesis 1 Summary:

  + middle/high income people are **less mypoic** than low income people
  + middle/high income people **with general trust even less mypoic** than counterparts with no general trust
  + low income people are **even more mypoic with no general trust**

##poor = (≤ 4)
```{r, echo=FALSE}
hyp_1 <- pca_val_dataNOINCOME %>% filter(!is.na(income)) %>%
          mutate(low_income = ifelse(income <=4, T, F)) %>%
          group_by(gTrust, low_income) %>% 
          summarise(discounting_factor = mean(pc1, na.rm = T)) 
hyp_1

ggplot(data=hyp_1, aes(x=gTrust, y=discounting_factor, colour=low_income, group=low_income)) +
    geom_line() + geom_point() + xlab("") +
    theme(legend.position="bottom", axis.text.x  = element_text(face="bold")) + 
    ggtitle("Average Discounting Factor by Group:\nGeneral Trust & Income")
```
  
##other definitions of poor

###poor = (≤ 3)
```{r, echo=FALSE}
hyp_1 <- pca_val_dataNOINCOME %>% filter(!is.na(income)) %>%
          mutate(low_income = ifelse(income <=3, T, F)) %>%
          group_by(gTrust, low_income) %>% 
          summarise(discounting_factor = mean(pc1, na.rm = T)) 
hyp_1
# ggplot(data=hyp_1, aes(x=gTrust, y=discounting_factor, fill=low_income)) +
#     geom_bar(stat="identity", position=position_dodge(), colour="black") + 
#   theme(legend.position="bottom", axis.text.x  = element_text(face="bold")) + xlab("") +
#   ggtitle("Discounting Factor by\nGeneral Trust & Income")
```

###poor = (≤ 2)
```{r, echo=FALSE}
hyp_1 <- pca_val_dataNOINCOME %>% filter(!is.na(income)) %>%
          mutate(low_income = ifelse(income <=2, T, F)) %>%
          group_by(gTrust, low_income) %>% 
          summarise(discounting_factor = mean(pc1, na.rm = T)) 
hyp_1
# ggplot(data=hyp_1, aes(x=gTrust, y=discounting_factor, fill=low_income)) +
#     geom_bar(stat="identity", position=position_dodge(), colour="black") + 
#   theme(legend.position="bottom", axis.text.x  = element_text(face="bold")) + xlab("") +
#   ggtitle("Discounting Factor by\nGeneral Trust & Income")
```

###poor = (≤ 1)
```{r, echo=FALSE}
hyp_1 <- pca_val_dataNOINCOME %>% filter(!is.na(income)) %>%
          mutate(low_income = ifelse(income <=1, T, F)) %>%
          group_by(gTrust, low_income) %>% 
          summarise(discounting_factor = mean(pc1, na.rm = T)) 
hyp_1
# ggplot(data=hyp_1, aes(x=gTrust, y=discounting_factor, fill=low_income)) +
#     geom_bar(stat="identity", position=position_dodge(), colour="black") + 
#   theme(legend.position="bottom", axis.text.x  = element_text(face="bold")) + xlab("") +
#   ggtitle("Discounting Factor by\nGeneral Trust & Income")
```

\
[back to table of contents](#TOC)

#Hypothesis 2: neighborhood trust not different 

**indeed** there is no significant variation across income level for neighborhood trust:
```{r, echo=FALSE, fig.width=14}
hood <- wvs_data %>% filter(!is.na(nTrust), !is.na(income)) %>%
        select(nTrust, income) 
ggplot(data=hood, aes(x=income, fill=nTrust)) +
    geom_bar(stat="bin", position=position_dodge()) + 
  theme(legend.position="bottom", axis.text.x  = element_text(face="bold")) + xlab("") + 
  scale_x_discrete(breaks=c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"))  
```

\
[back to table of contents](#TOC)

#Hypothesis 3: poor people with neighborhood trust less myopic 

###including income for calculation of TD proxy
```{r, echo=FALSE}
#neighborhood trust
fit1 <- lm(pc1 ~ nTrust, data = pca_val_data)
# summary(fit1)

#neighborhood trust controlling for general trust (additave model... IVs very different)
fit2 <- lm(pc1 ~ nTrust + gTrust, data = pca_val_data)
# summary(fit2)

#neighborhood trust controlling for general trust (interactions between IVs)
fit3 <- lm(pc1 ~ nTrust * gTrust, data = pca_val_data)
# summary(fit3)
```

```{r, eval=FALSE}
(1) <- lm(pc1 ~ nTrust)
(2) <- lm(pc1 ~ nTrust + gTrust)
(3) <- lm(pc1 ~ nTrust * gTrust)
```

```{r, results='asis', echo=FALSE}
stargazer(fit1, fit2, fit3, title="Regression Results Including Income", align=TRUE, type="html")
```

###NOT including income
```{r, echo=FALSE}
#neighborhood trust
fit1 <- lm(pc1 ~ nTrust, data = pca_val_dataNOINCOME)
# summary(fit1)

#neighborhood trust controlling for general trust (additave model... IVs very different)
fit2 <- lm(pc1 ~ nTrust + gTrust, data = pca_val_dataNOINCOME)
# summary(fit2)

#neighborhood trust controlling for general trust (interactions between IVs)
fit3 <- lm(pc1 ~ nTrust * gTrust, data = pca_val_dataNOINCOME)
# summary(fit3)
```

```{r, eval=FALSE}
(1) <- lm(pc1 ~ nTrust)
(2) <- lm(pc1 ~ nTrust + gTrust)
(3) <- lm(pc1 ~ nTrust * gTrust)
```

```{r, results='asis', echo=FALSE}
stargazer(fit1, fit2, fit3, title="Regression Results NOT Including Income", align=TRUE, type="html")
```

\
[back to table of contents](#TOC)

##means of TD proxy
broken down by neighborhood trust and general trust. **indeed** the case that effect of low general trust on temporal discounting is buffered by increasing neighborhood trust!! 

###including income for calculation of TD proxy
```{r, echo=FALSE}
pca_val_data %>% group_by(nTrust, gTrust) %>% 
  summarise(discounting_factor = mean(pc1, na.rm = T)) 
```

###NOT including income 
```{r, echo=FALSE}
pca_val_dataNOINCOME %>% group_by(nTrust, gTrust) %>% 
  summarise(discounting_factor = mean(pc1, na.rm = T)) 
```

\
[back to table of contents](#TOC)

