
---
title: "WVS: archival data"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("/git_repositories/trust/WVS_data/scripts/load_libraries.R")
source("/git_repositories/bangla/scripts/plotting_functions.R")
wvs_data <- readRDS("/git_repositories/trust/WVS_data/data/in_process_data/fulldata_cleaned.RDS") %>% 
        filter(!is.na(income))
```

#generalized trust 

overall distribution is as follows: 
```{r, echo=FALSE, fig.width=12, fig.height=3}
plot_percent(wvs_data, "gTrust", coordflippin = T, removeNAs = F)
```

##by income
```{r, echo=FALSE, fig.height=7, fig.width=9}
# ggplot(wvs_data %>% filter(!is.na(gTrust)), 
#        aes(x=gTrust, fill = gTrust)) + geom_bar(stat="bin") + 
# #   geom_bar(stat="bin", colour = "black", fill = "#F0E442") + 
#   facet_grid(income ~ .) + theme(axis.text.x = element_blank()) + 
#   scale_fill_discrete(name="General Trust")

#box and whisks
# ggplot(wvs_data %>% filter(!is.na(gTrust)), 
#        aes(x=gTrust, y=income, fill=gTrust)) + 
#   geom_boxplot() + guides(fill=FALSE) + coord_flip()

#dists by density
# ggplot(wvs_data %>% filter(!is.na(gTrust)), aes(x=income, colour=gTrust)) + 
#     geom_density() + scale_x_continuous(breaks=seq(0, 10, 1))

# ggplot(wvs_data %>% filter(!is.na(gTrust)), aes(x=income, fill=gTrust)) + 
#     geom_density(alpha=.5) + scale_x_continuous(breaks=seq(0, 10, 1)) + 
#     scale_fill_discrete(name="General Trust") + 
#     ggtitle("General Trust by Income")

income <- wvs_data %>% filter(!is.na(gTrust)) %>% group_by(income, gTrust) %>% 
            summarize(number = n()) %>% group_by(income) %>% 
            mutate(total = sum(number), percent = round(100*number/total, digits = 0))

ggplot(income, aes(x=income, y=percent, fill=gTrust)) +
    geom_histogram(binwidth=.5, alpha=.5, stat="identity") + 
    scale_x_continuous(breaks=seq(0, 10, 1)) 

# ggplot(income, aes(x=income, y=percent, fill=gTrust)) +
#     geom_histogram(binwidth=.25, alpha=.5, stat="identity", position="dodge") + 
#     scale_x_continuous(breaks=seq(0, 10, 1))

#dists by hists
# ggplot(wvs_data %>% filter(!is.na(gTrust)), aes(x=income, fill=gTrust)) +
#     geom_histogram(binwidth=.5, alpha=.5, position="identity") + 
#     scale_x_continuous(breaks=seq(0, 10, 1))

# ggplot(wvs_data %>% filter(!is.na(gTrust)), aes(x=income, fill=gTrust)) +
#     geom_histogram(binwidth=.5, position="dodge") + 
#     scale_x_continuous(breaks=seq(0, 10, 1))
```


```{r, eval=FALSE, echo=FALSE, fig.width=12, fig.height=3}
##by varying definitions of income
**less and less trust** relatively when changing income definition:

plot_percent(wvs_data %>% filter(lowIncome_4), "gTrust", coordflippin = T) + 
  ggtitle("Income ≤ 4") + theme(plot.title = element_text(face="bold"))
plot_percent(wvs_data %>% filter(lowIncome_3), "gTrust", coordflippin = T) +
  ggtitle("Income ≤ 3") + theme(plot.title = element_text(face="bold"))
plot_percent(wvs_data %>% filter(lowIncome_2), "gTrust", coordflippin = T) +
  ggtitle("Income ≤ 2") + theme(plot.title = element_text(face="bold"))
plot_percent(wvs_data %>% filter(lowIncome_1), "gTrust", coordflippin = T) +
  ggtitle("Income = 1") + theme(plot.title = element_text(face="bold"))
```

```{r, echo=FALSE, fig.width=12, fig.height=5}
# general <- wvs_data %>% filter(gTrust == "Most people can be trusted")
# plot_percent2(general, "gTrust", "lowIncome_4", coordflippin = F) + 
#   scale_fill_discrete(name="Low Income") + ggtitle("Low Income ≤ 4 \non scale of 10")
# plot_percent2(general, "gTrust", "lowIncome_3", coordflippin = F) + 
#   scale_fill_discrete(name="Low Income") + ggtitle("Low Income ≤ 3 \non scale of 10")
# plot_percent2(general, "gTrust", "lowIncome_2", coordflippin = F) + 
#   scale_fill_discrete(name="Low Income") + ggtitle("Low Income ≤ 2 \non scale of 10")
# plot_percent2(general, "gTrust", "lowIncome_1", coordflippin = F) + 
#   scale_fill_discrete(name="Low Income") + ggtitle("Low Income = 1 \non scale of 10"); remove(general)
```

```{r, echo=FALSE, eval=FALSE, fig.width=14, fig.height=7}
##by continent
ggplot(wvs_data %>% filter(!is.na(continent), !is.na(gTrust)), 
       aes(x=gTrust, fill = gTrust)) + geom_bar(stat="bin") + 
#   geom_bar(stat="bin", colour = "black", fill = "#F0E442") + 
  facet_grid(income ~ continent) + theme(axis.text.x = element_blank()) + 
  scale_fill_discrete(name="General Trust")
```

\
[back to table of contents](#TOC)

#community trust 

overall distribution is as follows: 
```{r, echo=FALSE, fig.width=12, fig.height=3}
plot_percent(wvs_data, "nTrust", coordflippin = T)
```

community trust **does not vary across income**. nearly identical proportional distribution: 
```{r, echo=FALSE, fig.width=14, fig.height=7}
# ggplot(wvs_data %>% filter(!is.na(nTrust)), 
#        aes(x=nTrust, fill = nTrust)) + geom_bar(stat="bin") + 
# #   geom_bar(stat="bin", colour = "black", fill = "#F0E442") + 
#   facet_grid(income ~ .) + theme(axis.text.x = element_blank()) + 
#   scale_fill_discrete(name="Community Trust")

# ggplot(wvs_data %>% filter(!is.na(nTrust)), aes(x=income, fill=nTrust)) + 
#     geom_density(alpha=.3) + scale_x_continuous(breaks=seq(0, 10, 1)) + 
#     scale_fill_discrete(name="Community Trust") + 
#     ggtitle("Community Trust by Income")

# ggplot(wvs_data %>% filter(!is.na(nTrust)), aes(x=income, fill=nTrust)) +
#     geom_histogram(binwidth=.5, alpha=.5, position="identity") + 
#     scale_x_continuous(breaks=seq(0, 10, 1)) +
#     ggtitle("Community Trust by Income")

# ggplot(wvs_data %>% filter(!is.na(nTrust)), aes(x=income, fill=nTrust)) +
#     geom_histogram(binwidth=.5, position="dodge") + 
#     scale_x_continuous(breaks=seq(0, 10, 1))

income2 <- wvs_data %>% filter(!is.na(nTrust)) %>% group_by(income, nTrust) %>% 
            summarize(number = n()) %>% group_by(income) %>% 
            mutate(total = sum(number), percent = round(100*number/total, digits = 0))

ggplot(income2, aes(x=income, y=percent, fill=nTrust)) +
    geom_histogram(binwidth=.5, alpha=.5, stat="identity") + 
    scale_x_continuous(breaks=seq(0, 10, 1)) 
```
\
[back to table of contents](#TOC)


#generalized trust vis-a-vis 5 factors

##happiness

overall distribution is as follows: 
```{r, echo=FALSE, fig.width=12, fig.height=3}
plot_percent(wvs_data, "happy", coordflippin = T)
```

```{r, echo=FALSE}
# happy <- wvs_data %>% filter(!is.na(gTrust), !is.na(happy))
happy <- wvs_data %>% filter(!is.na(gTrust), !is.na(happy)) %>%
          mutate(happy = ifelse(happy %in% c("Very happy", "Rather happy"), T, F))
happy_glm <- glm(gTrust~happy, data = happy, family = binomial)
```
####glm(gTrust ~ happy)
```{r, results='asis', echo=FALSE}
stargazer(happy_glm, type="html") #summary(happy_glm)
# exp(coef(happy_glm)) #odds ratios
```

####probabilities
```{r, echo=FALSE}
exp(coef(happy_glm))/(1 + exp(coef(happy_glm))) #probabilities
paste0("Most people can be trusted = 0,", " Need to be very careful = 1" )
```
**takeaway**: someone who is happy has a 37.5% likelihood of having low generalized trust
\
[back to table of contents](#TOC)


##health
overall distribution is as follows: 
```{r, echo=FALSE, fig.width=12, fig.height=3}
plot_percent(wvs_data, "health", coordflippin = T)
```

```{r, echo=FALSE}
health <- wvs_data %>% filter(!is.na(gTrust), !is.na(health), health != "No answer")
# health <- wvs_data %>% filter(!is.na(gTrust), !is.na(health)) %>%
#           mutate(health = ifelse(health %in% c("Very happy", "Rather happy"), T, F))
health_glm <- glm(gTrust~health, data = health, family = binomial)
```
####glm(gTrust ~ happy)
```{r, results='asis', echo=FALSE}
stargazer(health_glm, type="html") #summary(health_glm)
# exp(coef(health_glm)) #odds ratios
```

####probabilities
```{r, echo=FALSE}
exp(coef(health_glm))/(1 + exp(coef(health_glm))) #probabilities
paste0("Most people can be trusted = 0,", " Need to be very careful = 1" )
```
**takeaway**: poorer the health, higher probability of having low generalized trust.
\
[back to table of contents](#TOC)

##life 

overall distribution is as follows: 
```{r, echo=FALSE, fig.width=12, fig.height=3}
plot_percent(wvs_data, "life", coordflippin = T)
```

```{r, echo=FALSE}
life <- wvs_data %>% filter(!is.na(gTrust), !is.na(life))
# health <- wvs_data %>% filter(!is.na(gTrust), !is.na(health)) %>%
#           mutate(health = ifelse(health %in% c("Very happy", "Rather happy"), T, F))
life_glm <- glm(gTrust~life, data = life, family = binomial)
```
####glm(gTrust ~ happy)
```{r, results='asis', echo=FALSE}
stargazer(life_glm, type="html") #summary(life_glm)
# exp(coef(life_glm)) #odds ratios
```

####probabilities
```{r, echo=FALSE}
exp(coef(life_glm))/(1 + exp(coef(life_glm))) #probabilities
paste0("Most people can be trusted = 0,", " Need to be very careful = 1" )
```
**takeaway**: lower than 6 on scale of life satisfaction comes with higher probability of having low generalized trust.
\
[back to table of contents](#TOC)

##finance
overall distribution is as follows: 
```{r, echo=FALSE, fig.width=12, fig.height=3}
plot_percent(wvs_data, "finance", coordflippin = T)
```

```{r, echo=FALSE}
finance <- wvs_data %>% filter(!is.na(gTrust), !is.na(finance))
# health <- wvs_data %>% filter(!is.na(gTrust), !is.na(health)) %>%
#           mutate(health = ifelse(health %in% c("Very happy", "Rather happy"), T, F))
finance_glm <- glm(gTrust~finance, data = finance, family = binomial)
```
####glm(gTrust ~ happy)
```{r, results='asis', echo=FALSE}
stargazer(finance_glm, type="html") #summary(finance_glm)
# exp(coef(life_glm)) #odds ratios
```

####probabilities
```{r, echo=FALSE}
exp(coef(finance_glm))/(1 + exp(coef(finance_glm))) #probabilities
paste0("Most people can be trusted = 0,", " Need to be very careful = 1" )
```
**takeaway**: lower than 7 on scale of satisfaction with financial situation comes with higher probability of having low generalized trust.
\
[back to table of contents](#TOC)

##edu
overall distribution is as follows: 
```{r, echo=FALSE, fig.width=12, fig.height=3}
plot_percent(wvs_data, "edu", coordflippin = T)
```

```{r, echo=FALSE}
edu <- wvs_data %>% filter(!is.na(gTrust), !is.na(edu))
# health <- wvs_data %>% filter(!is.na(gTrust), !is.na(health)) %>%
#           mutate(health = ifelse(health %in% c("Very happy", "Rather happy"), T, F))
edu_glm <- glm(gTrust~edu, data = edu, family = binomial)
```
####glm(gTrust ~ happy)
```{r, results='asis', echo=FALSE}
stargazer(edu_glm, type="html") #summary(edu_glm)
# exp(coef(edu_glm)) #odds ratios
```

####probabilities
```{r, echo=FALSE}
exp(coef(edu_glm))/(1 + exp(coef(edu_glm))) #probabilities
paste0("Most people can be trusted = 0,", " Need to be very careful = 1" )
```
**takeaway**: less education comes with higher probability of having low generalized trust.
\
[back to table of contents](#TOC)


#generalized trust + community trust vis-a-vis 5 factors

##happiness
```{r, eval=FALSE, echo=FALSE}
#interactions with cTrust
happy3 <- wvs_data %>% filter(!is.na(gTrust), !is.na(happy), !is.na(nTrust)) %>%
            mutate(happy = ifelse(happy %in% c("Very happy", "Rather happy"), T, F),
                   nTrust = ifelse(nTrust %in% c("Trust completely", "Trust somewhat"), T, F))

happy_glm3 <- glm(gTrust~happy+nTrust+(nTrust*happy), data = happy3, family = binomial)
summary(happy_glm3)
exp(coef(happy_glm3)) #odds ratios
exp(coef(happy_glm3))/(1 + exp(coef(happy_glm3))) #probabilities

```

##health

##life 

##finance

##edu
