
---
title: "WVS: correlational data"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("/git_repositories/trust/WVS_data/scripts/load_libraries.R")
source("/git_repositories/bangla/scripts/plotting_functions.R")
wvs_data <- readRDS("/git_repositories/trust/WVS_data/data/in_process_data/fulldata_cleaned.RDS") %>%
              filter(!is.na(income))
```

#generalized trust 

overall distribution is as follows: 
```{r, echo=FALSE, fig.width=12, fig.height=3}
plot_percent(wvs_data, "gTrust", coordflippin = T)
```

##by income
```{r, echo=FALSE, fig.height=7, fig.width=11}
# ggplot(wvs_data %>% filter(!is.na(gTrust)), 
#        aes(x=gTrust, fill = gTrust)) + geom_bar(stat="bin") + 
# #   geom_bar(stat="bin", colour = "black", fill = "#F0E442") + 
#   facet_grid(income ~ .) + theme(axis.text.x = element_blank()) + 
#   scale_fill_discrete(name="General Trust")

#box and whisks
# ggplot(wvs_data %>% filter(!is.na(gTrust)), 
#        aes(x=gTrust, y=income, fill=gTrust)) + 
#   geom_boxplot() + guides(fill=FALSE) + coord_flip()

#dists by density
# ggplot(wvs_data %>% filter(!is.na(gTrust)), aes(x=income, colour=gTrust)) + 
#     geom_density() + scale_x_continuous(breaks=seq(0, 10, 1))

ggplot(wvs_data %>% filter(!is.na(gTrust)), aes(x=income, fill=gTrust)) + 
    geom_density(alpha=.5) + scale_x_continuous(breaks=seq(0, 10, 1)) + 
    scale_fill_discrete(name="General Trust") + 
    ggtitle("General Trust by Income")

#dists by hists
# ggplot(wvs_data %>% filter(!is.na(gTrust)), aes(x=income, fill=gTrust)) +
#     geom_histogram(binwidth=.5, alpha=.5, position="identity") + 
#     scale_x_continuous(breaks=seq(0, 10, 1))

# ggplot(wvs_data %>% filter(!is.na(gTrust)), aes(x=income, fill=gTrust)) +
#     geom_histogram(binwidth=.5, position="dodge") + 
#     scale_x_continuous(breaks=seq(0, 10, 1))
```

\
[back to table of contents](#TOC)

##by varying definitions of income
**less and less trust** relatively when changing income definition:

```{r, echo=FALSE, fig.width=12, fig.height=3}
plot_percent(wvs_data %>% filter(lowIncome_4), "gTrust", coordflippin = T) + 
  ggtitle("Income ≤ 4") + theme(plot.title = element_text(face="bold"))
```

```{r, echo=FALSE, fig.width=12, fig.height=3}
plot_percent(wvs_data %>% filter(lowIncome_3), "gTrust", coordflippin = T) +
  ggtitle("Income ≤ 3") + theme(plot.title = element_text(face="bold"))
```

```{r, echo=FALSE, fig.width=12, fig.height=3}
plot_percent(wvs_data %>% filter(lowIncome_2), "gTrust", coordflippin = T) +
  ggtitle("Income ≤ 2") + theme(plot.title = element_text(face="bold"))
```

```{r, echo=FALSE, fig.width=12, fig.height=3}
plot_percent(wvs_data %>% filter(lowIncome_1), "gTrust", coordflippin = T) +
  ggtitle("Income = 1") + theme(plot.title = element_text(face="bold"))
```


```{r, echo=FALSE, fig.width=12, fig.height=5}
# general <- wvs_data %>% filter(gTrust == "Most people can be trusted")
# plot_percent2(general, "gTrust", "lowIncome_4", coordflippin = F) + 
#   scale_fill_discrete(name="Low Income") + ggtitle("Low Income ≤ 4 \non scale of 10")
# plot_percent2(general, "gTrust", "lowIncome_3", coordflippin = F) + 
#   scale_fill_discrete(name="Low Income") + ggtitle("Low Income ≤ 3 \non scale of 10")
# plot_percent2(general, "gTrust", "lowIncome_2", coordflippin = F) + 
#   scale_fill_discrete(name="Low Income") + ggtitle("Low Income ≤ 2 \non scale of 10")
# plot_percent2(general, "gTrust", "lowIncome_1", coordflippin = F) + 
#   scale_fill_discrete(name="Low Income") + ggtitle("Low Income = 1 \non scale of 10"); remove(general)
```

\
[back to table of contents](#TOC)

##by continent

```{r, echo=FALSE, fig.width=14, fig.height=7}
ggplot(wvs_data %>% filter(!is.na(continent), !is.na(gTrust)), 
       aes(x=gTrust, fill = gTrust)) + geom_bar(stat="bin") + 
#   geom_bar(stat="bin", colour = "black", fill = "#F0E442") + 
  facet_grid(income ~ continent) + theme(axis.text.x = element_blank()) + 
  scale_fill_discrete(name="General Trust")
```

\
[back to table of contents](#TOC)

#community trust 
community trust **does not vary across income**. nearly identical proportional distribution: 
```{r, echo=FALSE, fig.width=14, fig.height=7}
# ggplot(wvs_data %>% filter(!is.na(nTrust)), 
#        aes(x=nTrust, fill = nTrust)) + geom_bar(stat="bin") + 
# #   geom_bar(stat="bin", colour = "black", fill = "#F0E442") + 
#   facet_grid(income ~ .) + theme(axis.text.x = element_blank()) + 
#   scale_fill_discrete(name="Community Trust")

# ggplot(wvs_data %>% filter(!is.na(nTrust)), aes(x=income, fill=nTrust)) + 
#     geom_density(alpha=.3) + scale_x_continuous(breaks=seq(0, 10, 1)) + 
#     scale_fill_discrete(name="Community Trust") + 
#     ggtitle("Community Trust by Income")

# ggplot(wvs_data %>% filter(!is.na(nTrust)), aes(x=income, fill=nTrust)) +
#     geom_histogram(binwidth=.5, alpha=.5, position="identity") + 
#     scale_x_continuous(breaks=seq(0, 10, 1)) +
#     ggtitle("Community Trust by Income")

ggplot(wvs_data %>% filter(!is.na(nTrust)), aes(x=income, fill=nTrust)) +
    geom_histogram(binwidth=.5, position="dodge") + 
    scale_x_continuous(breaks=seq(0, 10, 1))
```

\
[back to table of contents](#TOC)


#generalized trust with 5 factors

```{r, eval=FALSE, echo=FALSE}
# yo <- wvs_data %>% dplyr::select(gTrust, happy) %>% 
#         filter(!is.na(gTrust), !is.na(happy)) 
# plot(yo)
```

#generalized trust + community trust with 5 factors
Show general trust and community trust across 5 factors.... 
```{r, eval=FALSE, echo=FALSE}
??
```

•	

